Optimizing the power of adaptive seamless designs using Bayesian Optimization

### 2020-10-07 main.tex
update plots
calc grid results for mbo
improve plots, mbo grid

% own packages
\usepackage{siunitx}
\usepackage{enumitem}
% tikz
\usepackage{tikz}
% we want ER + above/below + left/right
\usetikzlibrary{er,arrows, chains, fit, positioning, calc, shapes}

@@

@@

The strategies regarding treatment selection for the second stage in the two-phase trial design, following the concept of adaptive seamless designs discussed in Section~\ref{sec:adaptive_seamless_designs}, and their corresponding parameters that are used in the simulation study are given in Table~\ref{tab:selection_strategies} and Table~\ref{tab:search_space}, respectively.
The strategies 1, 2, 3, and \emph{all} select the $k$ best strategies according to their respective test statistics in the first stage (with \emph{all} representing all $k=4$ treatments besides the control). The strategies \emph{eps} and \emph{thresh} represent strategies with a flexible number of treatments taken to the second stage. In Table~\ref{tab:search_space} the ranges for these two parameters and for the proportion of patients (ratio $r$) allocated to the second stage are given.
\begin{table}[h]
  \caption{Overview of selection strategies to determine which trial arms are kept for second stage}
  \label{tab:selection_strategies}
  \centering
  \begin{tabular}{ll}
  \hline
  Notation & Procedure of selection strategy  \\
  \hline
  \emph{all}     & Select all arms  \\
  $\{1,2,3\}$    & Select 1, 2 or 3 arms, respectively, according to maximal test statistic \\
  \emph{eps}     & Select all arms with test statistic less than \emph{eps} (epsilon) below maximal test statistic \\
  \emph{thresh}     & Select all arms with test statistic larger than the value \emph{thresh} (threshold) \\
  \hline
  \end{tabular}
\end{table}
\begin{table}[h]
  \caption{Parameters for the selection strategies representing the search space of trial designs}
  \label{tab:search_space}
  \centering
  \begin{tabular}{ll}
  \hline
  Parameter         & Range \\
  \hline
  Selection strategy & $\{\text{all}, 1, 2, 3, \text{eps}, \text{thresh} \}$ \\
  $r$ (ratio)        & $(0,1)$ \\
  eps (epsilon)            & $[0,4]$ \\
  thresh (threshold)          & $[0,10]$ \\
  \hline
  \end{tabular}
\end{table}

@@

\newpage
\phantom{aaaa}
\end{document}

>>>>

% own packages
\usepackage{siunitx}
\usepackage{enumitem}
\usepackage{placeins} %floatbarrier
% tikz
\usepackage{tikz}
% we want ER + above/below + left/right
\usetikzlibrary{er,arrows, chains, fit, positioning, calc, shapes}

@@

\makeatletter
\let\newtitle\@title
\makeatother

@@

The strategies regarding treatment selection for the second stage in the two-phase trial design, following the concept of adaptive seamless designs discussed in Section~\ref{sec:adaptive_seamless_designs}, and their corresponding parameters that are used in the simulation study are given in Table~\ref{tab:selection_strategies} and Table~\ref{tab:search_space}, respectively.
The strategies 1, 2, 3, and \emph{all} select the $k$ best strategies according to their respective test statistics in the first stage (with \emph{all} representing all $k=4$ treatments besides the control). The strategies \emph{eps} and \emph{thresh} represent strategies with a flexible number of treatments taken to the second stage. In Table~\ref{tab:search_space} the ranges for these two parameters and for the proportion of patients (ratio $r$) allocated to the second stage are given.
\begin{table}[h]
  \caption{Overview of selection strategies to determine which trial arms are kept for second stage}
  \label{tab:selection_strategies}
  \centering
  \begin{tabular}{ll}
  \hline
  Notation       & Procedure of selection strategy  \\
  \hline
  \emph{all}     & Select all arms  \\
  $\{1,2,3\}$    & Select 1, 2 or 3 arms, respectively, according to maximal test statistic \\
  \emph{eps}     & Select all arms with test statistic less than $\epsilon$ (epsilon) below maximal test statistic \\
  \emph{thresh}  & Select all arms with test statistic larger than the value $\tau$ (threshold) \\
  \hline
  \end{tabular}
\end{table}
\begin{table}[h]
  \caption{Parameters for the selection strategies representing the search space of trial designs}
  \label{tab:search_space}
  \centering
  \begin{tabular}{ll}
  \hline
  Parameter                        & Range \\
  \hline
  Selection strategy               & $\{\text{all}, 1, 2, 3, \text{eps}, \text{thresh} \}$ \\
  $r$ (ratio)                      & $(0,1)$ \\
  $\epsilon$ (only for \emph{eps}) & $[0,4]$ \\
  $\tau$ (onlt for \emph{thresh})  & $[0,10]$ \\
  \hline
  \end{tabular}
\end{table}

@@

\newpage
\phantom{aaaa}
%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
\clearpage
\begin{center}
\textbf{\large Supplemental Materials: \newtitle}
\end{center}
\FloatBarrier
%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_opt_path.pdf}
\caption{%
  Optimization curves of each optimization run and the mean of all runs drawn as a black line.
  }
\label{fig:plot_opt_path} 
\end{figure}

\end{document}
